The Heavy Photon Search Test Detector

### 2014-03-10 hps-testrun-nim.tex
Centering pictures.

\section{Detector Overview}
\label{detector}
\begin{center}
{\small
\begin{figure*}[ht]
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{figure*}
}
\end{center}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at an energy of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam and the degraded electrons after the target are spread out horizontally by 
the analyzing magnet constitute a "dead zone" which must be completely avoided. The apparatus is 
split vertically $15$~mrad above and below the beam plane and the beam is transported in vacuum 
to minimize beam-gas interaction backgrounds. Even so, background occupancy in the detectors 
remain high and are dominated by the degraded primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger comes from a PbWO$_{4}$ crystal calorimeter. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the HPS Test apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

@@

During the Test run, both halves were held in place by four vertical bars attached to an above rail, 
placing the front face of the crystals 147~cm from the upstream edge of the magnet and with a 
8.7~cm gap between the innermost edge of the crystals in the two halves.
\begin{center}
{\small
\begin{figure*}[htb]
\includegraphics[width=0.45\textwidth]{figures/ECal}
\includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
\caption{Rendered layout view (left) and the ECal assembly on the beam line (right).}
\label{fig:ecal}
\end{figure*}
}
\end{center}

\subsection{Signal readout}
\label{sec:fadc}
After a 2:1 signal splitter, $1/3$ of an amplified APD signal ($2/3$ is sent to a timing module) is fed to a 
single channel of a JLab flash ADC (FADC) board~\cite{fadc}, 
see Fig~.\ref{fig:fadc}.
\begin{figure}[]
\begin{center}
{\small
\includegraphics[width=5cm]{figures/FADC250_Photo_001.jpg}
\caption{The JLab FADC250 VXS module.}
\label{fig:fadc}
}
\end{center}
\end{figure}
The FADC boards are high speed VXS modules digitizing up to 16 APD signals 
at 250~MHz and storing samples in 8~$\mu$s deep pipelines with 12-bit resolution. 
When a trigger is received, the part 
of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
threshold (for the Test run this was set to $\approx70$~MeV) are 
summed and stored in a 17-bit register for readout as described in Fig.~\ref{fig:hps_trigger_data}.
This scheme significantly compresses the data output of the FADC. During offline data analysis, a 
calibrated pedestal value is subtracted to obtain the actual summed energy.
Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test run to read out the top 
(bottom) half of the ECal.
In the Test run 385 out of 442 modules (87\%) was used in offline reconstruction, 39 modules were 
disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
excessive noise) and 18 was masked offline due to noise. 
\begin{figure}[]
\begin{center}
{\small
\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
\caption{The two different readout modes of the FADC used in the Test run.}
\label{fig:hps_trigger_data}
}
\end{center}
\end{figure}

>>>>

\section{Detector Overview}
\label{detector}
{\small
\begin{figure*}[t]
\begin{center}
    \includegraphics[width=0.8\textwidth]{figures/hps_testrun_rendering}
\caption{Rendering of the HPS Test apparatus installed on the beam line.}
\label{fig:testrundetector}
\end{center}
\end{figure*}
}
The HPS Test apparatus was designed to run in Hall~B at JLab using the CEBAF electron beam, a 
499~MHz beam, at an energy of 2.2 and 6.6~GeV and currents between 200 and 600~nA.  
The overall design of the experiment follows from the kinematics of \Aprime{} production which 
typically results in final state particles within a few degrees of the incoming beam, especially at low 
$m_{\textrm{A}^\prime}$. Detectors must therefore be placed close to the beam. 
The intense electron beam and the degraded electrons after the target are spread out horizontally by 
the analyzing magnet constitute a "dead zone" which must be completely avoided. The apparatus is 
split vertically $15$~mrad above and below the beam plane and the beam is transported in vacuum 
to minimize beam-gas interaction backgrounds. Even so, background occupancy in the detectors 
remain high and are dominated by the degraded primary beam, so high rate detectors, a fast trigger, 
and excellent time tagging are required to minimize their impact.  
At masses below $2 m_\mu$ only decays to electrons are allowed, so the key trigger comes from a PbWO$_{4}$ crystal calorimeter. 
 %\begin{multicols}{2}
\begin{center}
\begin{table*}[t]
{\small
\caption{Overview of the coverage, segmentation and performance of the HPS Test detector. }
\begin{tabular}{lccccccc}
\hline 
System & Coverage & \# channels & ADC & Time resolution & \# layers & Segmentation & Performance \\
 & (mrad) &  & (bit) & (ns) &  &  &  \\
\hline
SVT & $15<\theta_{y} < XXXX$ & 12800 & 14 & $\approx 2$~ns & 5  & $\approx 120~\mu$m $r-\phi$ & $\sigma_{d0,y}  \approx 100~\mu$m \\
& &  &  &  & (stereo layers) & $\approx 6~\mu$m $z$ & $\sigma_{d0,x} \approx 300~\mu$m \\
& &  &  &  &  &  & $\sigma_{d0,z}\approx 1$~mm \\
\hline
ECal & $15<\theta_{y} < XXXX$ & 442 & 12 & 4~ns & 1 & $1.3\times1.3$~cm$^2$  & $\sigma(E)/E \approx 4.5\%$ \\ 
 &  &  &  &  &  & $1.6\times1.6$~cm$^2$  &  \\ 
\hline
\end{tabular}
\label{tab:detector-overview}
}
\end{table*}
\end{center}
%\end{multicols}
A rendering of the HPS Test apparatus installed on the beam line is shown in 
Fig.~\ref{fig:testrundetector} and an overview of the coverage, segmentation and performance is 
given in Tab.~\ref{tab:detector-overview}.

@@

During the Test run, both halves were held in place by four vertical bars attached to an above rail, 
placing the front face of the crystals 147~cm from the upstream edge of the magnet and with a 
8.7~cm gap between the innermost edge of the crystals in the two halves.
{\small
\begin{figure*}[htb]
\begin{center}
\includegraphics[width=0.45\textwidth]{figures/ECal}
\includegraphics[width=0.45\textwidth]{figures/ecal_picture_beamline}
\caption{Rendered layout view (left) and the ECal assembly on the beam line (right).}
\label{fig:ecal}
\end{center}
\end{figure*}
}

\subsection{Signal readout}
\label{sec:fadc}
After a 2:1 signal splitter, $1/3$ of an amplified APD signal ($2/3$ is sent to a timing module) is fed to a 
single channel of a JLab flash ADC (FADC) board~\cite{fadc}, 
see Fig~.\ref{fig:fadc}.
\begin{figure}[]
\begin{center}
{\small
\includegraphics[width=4cm]{figures/FADC250_Photo_001.jpg}
\caption{The JLab FADC250 VXS module.}
\label{fig:fadc}
}
\end{center}
\end{figure}
The FADC boards are high speed VXS modules digitizing up to 16 APD signals 
at 250~MHz and storing samples in 8~$\mu$s deep pipelines with 12-bit resolution. 
When a trigger is received, the part 
of the pipeline from 5 samples before and 30 after the signal crossed a programmable 
threshold (for the Test run this was set to $\approx70$~MeV) are 
summed and stored in a 17-bit register for readout as described in Fig.~\ref{fig:hps_trigger_data}.
This scheme significantly compresses the data output of the FADC. During offline data analysis, a 
calibrated pedestal value is subtracted to obtain the actual summed energy.
Two 20-slot VXS crates with 14 (13) FADC boards were employed in the Test run to read out the top 
(bottom) half of the ECal.
In the Test run 385 out of 442 modules (87\%) was used in offline reconstruction, 39 modules were 
disabled or not read out (no FADC channel available, no APD bias voltage or masked out due to 
excessive noise) and 18 was masked offline due to noise. 
\begin{figure}[]
\begin{center}
{\small
\includegraphics[width=8cm]{figures/fadc_datapath_diagram.png}
\caption{The two different readout modes of the FADC used in the Test run.}
\label{fig:hps_trigger_data}
}
\end{center}
\end{figure}
